---
title: "Data Memo and Approval"
author: "Xamantha Laos Cueva"
output:
  html_document:
    toc: true
    toc_float: true
    highlight: "tango"
---

<!-- Set global options for R code chunks -->

```{r global-settings, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
library(readr)
library(arrow)
library(skimr)

```

## ABOUT THE DATA

**Source:** I have obtained the Data from Kaggle from a competition called "[Predict Youtube Video Likes](https://www.kaggle.com/c/kaggle-pog-series-s01e01/data)." The data has been compiled by Kaggle, which provides a strong trust on its validity, and it is a compilation of metrics of over 90,000 Youtube Videos.

**General Facts:** As shown below, the data has 92,275 rows and 20 variables.

```{r}
#data
data <- read_parquet("train.parquet")

#number of rows and columns
nrow(data)
ncol(data)
```

**Considerations:**

1.  Kaggle provides both a training and a test set for the purpose of the competition. However, I will only make use of the training set (this will be split into a sub-training and test sets) to assess my models.

2.  The number of observations is very large. So far, it does not seem to cause problems when generating simple operations so I am planning to use all the observations. However, if advice by the instructor, I will take a sample of about 20,000 observations for my final project.

**Motivation:** I have picked this data set for the following reasons:

1.  I worked as a social manager for an Ed-Tech company for one year and part of my work was creating content. I was always wondering what were the aspects of social media that drive engagement, so I am very interesting on this data set and the fact that it would allow me to make models that attempt to solve the question.

2.  Unlike many other data sets, the one I have chosen is very clean and has several numeric metrics, which makes it a good candidate to use for modeling.

## TIMELINE

-   Data set loaded: As show before, the data set is already loaded.

-   Analysis: I am planning to start with my analysis (specifically my EDA) next week.

-   Model Building: I am planning to start building the models once my EDA is finished, which should take a maximum of one week.

## POTENTIAL RESEARCH QUESTIONS

Some of the potential research questions are:

-   What is the feature of a video that affects the most the number of likes the video get? (inferential)

-   Given that a video has [insert features here], how many likes should it expect? (predictive)

My questions will most likely be answered with a regression-based approach.

## APPENDIX

```{r}
skim_without_charts(data)

```
